Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
net aggr slide

\frame{
\frametitle{Network Aggregation}
	\begin{itemize}
		\item Share a condensed view of the network: A Network flow table
		\item Surpress network events such that aggregated network does not change: Reduce communication overhead
		\item Convert flow addtion/removal commands on aggregated network to actual network in an efficient way

>>>>

\frame{
\frametitle{Network Aggregation}
	\begin{itemize}		
		\item Definition - Create and publish one flow table (referred to as $nflow$) for a given network. (1) Support addition of flows to $nflow$ efficiently. (2) Handle intra-link failure efficiently, in such a way that $nflow$  does not change.
		\item $nflow$ schema $(port in, flow in, port out, flow out, priority, attributes)$
		\item Data structures\footnote{code @ https://github.com/MugiwaraLuffy/ACN/tree/master/simulator/src/graph}:
		\begin{itemize}
			\item Add $external$ $nodes$ to the network graph $G$
			\item Flow graphs: For each external node, $e$, we create/maintain a directed flow graph, $f_e$ as an overlay graph on $G$, rooted at $e$, which is the source. End host and other external nodes acts as sink. The flow in $f_e$ are divided at nodes among the incident links according to the flow tables at corresponding routers.
			\item Other data structures include: Path array, Link array 
		\end{itemize} 		
	\end{itemize}
}
